---
title: "Reproducing the manuscript design"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducing the manuscript design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The package ships the frozen design defaults and scenario definitions used in the SEARS 2.0 manuscript.

```{r}
library(SEARS2)
sears2_paper_defaults
sears2_paper_truth
head(sears2_paper_scenarios)
```

## Lightweight paper-scenario example

```{r}
x <- simulate_sears2_trial("C1-M2", strategy = "sears2", seed = 1001)
x$analysis
```

The exported simulator in version 0.1.0 is intentionally lightweight and covers the terminal comparative stage.
It does **not** reproduce the full 180,000-evaluation production engine, pre-randomization safety stage,
or latent-phenotype endpoint correlation. The scientific-development repository remains the source of truth
for the accepted manuscript production simulation.
